%-------------------------
% Optimized Resume for ATS
% Author: Husan Boymurodov
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{microtype}
\input{glyphtounicode}

%----------PAGE SETUP----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%----------SECTION FORMATTING----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%----------CUSTOM COMMANDS----------
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large #1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%==========BEGIN DOCUMENT==========
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Husan Boymurodov} \\ \vspace{4pt}
    \small
    \href{mailto:husayin2003@gmail.com}{husayin2003@gmail.com} $|$ 
    \href{tel:+601161337608}{+60 11 6133 7608} $|$ 
    \href{https://boymurodov.com}{\underline{boymurodov.com}} $|$
    \href{https://www.linkedin.com/in/husanboymurodov/}{\underline{LinkedIn}} $|$
    \href{https://github.com/husanboymurodov}{\underline{GitHub}} $|$
    \href{https://huggingface.co/husanboymurodov}{\underline{Hugging Face}} \\ \vspace{2pt}
    \textit{Software Engineer $|$ Available for roles from May 2026}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Malaya}{Kuala Lumpur, Malaysia}
      {Bachelor of Computer Science (Information Systems)}{2023 -- 2026}
      \resumeItemListStart
        \resumeItem{\textbf{CGPA: 3.26 / 4.00}}
        \resumeItem{\textbf{Extracurriculars}: Gold Medalist, 2025 MIQ Taekwondo Championship; Data Science Digital Race Participant.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineer Intern}{Feb 2026 -- May 2026}
      {AI Sales Dr Pte. Ltd. --- \href{https://ai-sales-dr.co}{\underline{ai-sales-dr.co}}}{Singapore (Remote)}
      \resumeItemListStart
        \resumeItem{Engineered and maintained scalable full-stack features using \textbf{TypeScript, Next.js, and Node.js} in a high-traffic production environment.}
        \resumeItem{Orchestrated backend infrastructure on \textbf{Google Cloud Platform (GCP)}, leveraging \textbf{Docker} and establishing automated \textbf{CI/CD} pipelines.}
        \resumeItem{Optimized backend automation workflows via \textbf{n8n} by restructuring logic nodes, reducing redundant API calls and increasing execution efficiency by 30\%.}
        \resumeItem{Managed API integrations with \textbf{Supabase}, ensuring data validation, consistency, and transactional integrity across services.}
        \resumeItem{Resolved critical application bugs and regressions, significantly strengthening system stability and uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {Information Technology Intern}{Mar 2022 -- Jul 2022}
      {British Management University --- \href{https://bmu-edu.uz}{\underline{bmu-edu.uz}}}{Tashkent, Uzbekistan}
      \resumeItemListStart
        \resumeItem{Developed and optimized university web infrastructure using \textbf{WordPress}, improving global site performance and user accessibility.}
        \resumeItem{Diagnosed and resolved hardware/software technical disruptions, ensuring continuous operational uptime for faculty and staff.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {MyWebsite --- Software Engineer Portfolio}{}
      \resumeItemListStart
        \resumeItem{A high-performance portfolio showcasing full-stack capabilities with a modern dark theme and interactive UI components.}
        \resumeItem{\textbf{Tech}: React 19, TypeScript, Vite, Docker, GCP Cloud Run, CSS Variables.}
        \resumeItem{\href{https://boymurodov.com}{\underline{Try it here}} $|$ \href{https://github.com/husanboymurodov/MyWebsite}{\underline{Show Code}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {FitHub --- Full-Stack Fitness Tracker}{}
      \resumeItemListStart
        \resumeItem{Comprehensive wellness platform to track workouts and nutrition with interactive data visualizations and secure authentication.}
        \resumeItem{\textbf{Tech}: Node.js, Express, MongoDB, EJS, Chart.js, Google Cloud Run.}
        \resumeItem{\href{https://fithub-app-745483922277.asia-southeast1.run.app/}{\underline{Try it here}} $|$ \href{https://github.com/muhammadariffahmi/fithub}{\underline{Show Code}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {OrderSmart --- ML Delivery Timing Predictor}{}
      \resumeItemListStart
        \resumeItem{Predictive analytics dashboard forecasting delivery delays based on weather, traffic, and logistical factors with high accuracy.}
        \resumeItem{\textbf{Tech}: Python, XGBoost, Gradio, Pandas, Hugging Face Spaces.}
        \resumeItem{\href{https://husanboymurodov-delivery-predictor.hf.space/}{\underline{Try it here}} $|$ \href{https://huggingface.co/spaces/husanboymurodov/delivery-predictor/tree/main}{\underline{Show Code}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {Customer Churn Prediction Model}{}
      \resumeItemListStart
        \resumeItem{Machine Learning classification model designed to identify at-risk customers and support retention analysis.}
        \resumeItem{\textbf{Tech}: Python, Scikit-learn, XGBoost, Hugging Face.}
        \resumeItem{\href{https://husanboymurodov-customer-churn-predictor.hf.space/}{\underline{Try it here}} $|$ \href{https://huggingface.co/spaces/husanboymurodov/customer-churn-predictor/tree/main}{\underline{Show Code}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Software Engineering}{: JavaScript, TypeScript, Python, Node.js, Express.js, Next.js, React, REST APIs} \\[3pt]
     \textbf{Cloud \& DevOps}{: GCP, Docker, CI/CD, Git, GitHub, Linux/UNIX, n8n Automation, Postman} \\[3pt]
     \textbf{Databases}{: SQL, Supabase, MongoDB} \\[3pt]
     \textbf{Data \& AI}{: Machine Learning, XGBoost, Hugging Face, LLMs (Ollama), Model Evaluation, Feature Engineering} \\[3pt]
     \textbf{Visualization}{: Tableau, Power BI}
    }}
 \end{itemize}

\end{document}
